The Effect of Elections and Prime Ministers on Discussion in the Australian Federal Parliament (1901--2018)

### 2018-12-15 outputs/docs/events/paper.Rmd
Add stop words graph and update appendix tables

header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage[table]{xcolor}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}

@@

elections <-
  read_csv("../../../outputs/misc/misc_elections.csv", col_types = cols())

governments <-
  read_csv("../../../outputs/misc/pm_dates.csv", col_types = cols())

@@

The recent digitisation of the Canadian Hansard, @BeelenEtc2017, has allowed increased analysis of Canadian parliament text records. For instance, @RheaultCochran2018 examined ideology and party polarisation in Britain and Canada using word embeddings. A digitised version of the UK Hansard has been available for some time. For instance, @Duthie2016 examined which politicians made supportive or aggressive statements toward other politicians, and @PetersonSpirling2018 examined polarisation. One exciting aspect of research using the UK Hansard has been linking text records with other datasets. For instance, @SlapinKirklandLazzaroLeslie2018 linked votes and speeches to examine grandstanding within parties. Another exciting aspect is that as digitisation methods improve, increasingly older UK records can be analysed, for instance, @Dimitruk2018 considered the effect of estate bills on prorogations in seventeenth century England. In New Zealand, @Curran2018 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950. And in the US, @GentzkowShapiroTaddy2018 examined congressional speech records from 1873 to 2016 to find that partisanship has risen in the past few decades.

@@

We use the official PDF release and the formatting of the Hansard records changes over time. We use scripts written in R [@R2018] to convert the PDFs into daily text records. An example of the workflow and some example scripts are provided in Appendix \@ref(hansardworkflow). Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate, especially for older records. An example of the latter issue is that 'the' is often parsed as 'thc'. These errors are corrected when they can be identified.

@@

<!-- One weakness of the LDA method is that it considers a 'bag of words' where the order of those words does not matter [@blei2012]. It is possible to extend the model to reduce the impact of the bag-of-words assumption and add conditionality to word order. -->

@@

Define $\theta_{dp}$ to be the proportion of topic $p$ on day $d$. Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P = 80$ are equal to the estimated values of $\theta_d$ from the CTM. We assume that the majority of variation in topics is across sitting periods, $s$, where a sitting period is defined as any group of days that are less than one week apart. Using this definition, there are 822 **[UPDATE]** sitting periods over the period 1901 to 2018 inclusive. Appendix \@ref(hansardsummarystatistics) contains more information about the sitting patterns over the course of the year, which have changed considerably since Federation.

@@

Table \@ref(tab:topwords) lists the top ten words associated with each of the 80 topics. The topics cover areas such as budgets, transport and infrastructure, war and conflict, health, education, agriculture, and trade. Similar to when topic models are run using the parliamentary text records of other countries, there are also some topics that appear to be about procedural or day-to-day matters, such as Topics 7 or 9. As expected, some topics seem to somewhat overlap with their content: for instance, Topics 4, 26, 28, 30 and 66 all relate to war and conflict.

@@

top_words %>% 
  kable("latex", booktabs = T, longtable = TRUE, caption = "Top words associated with each topic") %>%
  kable_styling(font_size = 8, latex_options = c("repeat_header")) %>% 
  footnote(general = "We display only the top ten words for each topic, but the topics are defined by probability distributions over all words.")

@@

```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with five topics highlighted", out.width = '100%'}
knitr::include_graphics("../../figures/topics_example.png")

@@

```{r threeexamples, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, for three periods", out.width = '100%'}
knitr::include_graphics("../../figures/topics_examples_three.pdf")

@@

```{r mugov, cache = TRUE, echo = FALSE, fig.cap = "prime minister level effects on selected topics.", out.width = '100%'}
knitr::include_graphics("../../figures/mu_gov.pdf")
```

```{r muelection, cache = TRUE, echo = FALSE, fig.cap = "Elections level effects on selected topics", out.width = '100%'}
knitr::include_graphics("../../figures/mu_election.pdf")
```

In Appendix \@ref(resilientresults) we show that our main findings are resilient to both fewer - 60 - and more - 100 - topics.

@@

Of the 36 prime ministers over this period, we find that 20 of them are significantly different to the prime minister that preceded them. However, four of these results -- the significance of the Page Premiership, the First Menzies Premiership, the Chifley Premiership and the Abbott Premiership -- are likely due to the short length of either the prime minister or the predecessor and should be ignored, leaving only 16. The earliest of these are the First Fisher Premiership, the Cook Premiership and the Third Fisher Premiership, which were different to the Second Deakin Premiership, the Second Fisher Premiership, and the Cook Premiership, respectively. To a certain extent this is likely due to changes due to World War I.

@@

By bringing a new dataset of what was said in the Australian Federal Parliament to bear for our analysis we are able to consider events over the full history of the Commonwealth of Australia. However even after cleaning the dataset remains imperfect and is more fit-for-purpose than of broad applicability. Future work could continue to improve the quality of this dataset. For instance, exploiting the availability of XML records to enhance the record parsed from the PDFs would enable the creation of a Hansard for research purposes that combined the best of both and would be used in a variety of research.

Using text as data allows us to conduct larger-scale analysis that would not be viable using less-automated approaches and so researchers may be able to identify associations and patterns that would otherwise have been overlooked. That said, the approach has well-known shortcomings and weaknesses, such as those documented by @GrimmerStewart2013. Our paper should thus be considered a complement to more detailed analysis such as qualitative methods and case studies. An example of one of the more glaring issues when using topic models is the need to interpret the topics. This can be difficult, especially when the number of topics is large, but in a dataset of the size that we have, a large number of topics is needed. Also, although topic modelling is an unsupervised machine learning technique, the inputs require fine-tuning. Most obviously the number of topics needs to be specified, but there are also more nuanced aspects to be aware of. For instance, selecting stop words for removal and which words to merge because of common co-location has an impact on the topics. Even after doing this there tend to be topics that are not overly meaningful, especially on their own. One way to get around using topic models is to use a supervised learning approach, such as that used by @AshMorelliOsnabru2018 in the context of New Zealand Hansard. Another is to use the words more directly, for instance word2vec and other approaches. As computational power become cheaper and more appropriate analytical methods, such as @Taddy2015 as applied in @GentzkowShapiroTaddy2018, are developed this becomes a more feasible options and future research could explore that direction.

@@

Watching our politicians at work can sometimes be a little disheartening. It can be hard to believe that not only are those in charge shouting insults that would not be tolerated in a schoolyard, but that we voted to put them there. Nonetheless, our work suggests that important topics are discussed in parliament. It is easy to look back and think that we live in uniquely tumultuous times, but our analysis suggests events have always driven debate and that periods of stability may be the exception. However, we do find that since the 1990s the effect of prime ministers and elections on the topics discussed in the Australian parliament does seem to be more pronounced than it used to be.

@@

The distribution of sitting days over the course of the year changes over time. It was initially more piecemeal. This can be seen by comparing the pattern of sitting days in the years to 1920 (Figure \@ref(fig:dayssattonineteentwenty)) with those in the 19 years from, and including, 2000 (Figure \@ref(fig:dayssatfromtwothousand)).

@@

## Example Hansard PDF to text record workflow {#hansardworkflow}
The exact scripts that we use are too long to provide here but are available on request. Instead here we provide example scripts that summarises the workflow to convert the PDFs to usable text datasets and may be a useful starting point for other researchers. The scripts are primarily based on: the \texttt{PDFtools} R package of @Ooms2018pdftools; the \texttt{tidyverse} R package of @Wickham2017; the \texttt{tm} R package of @FeinererHornik2018; the \texttt{lubridate} R package of @GrolemundWickham2011; the \texttt{tidytext} R package of @SilgeRobinson2016; and the \texttt{stringi} R package of @Gagolewski2018. The functions of those packages are augmented by: the \texttt{furrr} R package of @VaughanDancho2018; and the \texttt{tictoc} R package of @Izrailev2014. The \texttt{hunspell} R package of @Ooms2017 is used to help find spelling issues; and the \texttt{quanteda} R package of @Benoit2018 is used to compound multiword expressions.

**[Insert the example scripts.]**

The first step is to scrape the websites for the PDFs.

```{r scrapingexample, echo=TRUE, eval = FALSE}
name_of_address_to_visit <- c("wwww1", "wwww2")
name_of_where_to_save <- c("2017-02-01.pdf", "2017-02-02.pdf")

visit_address_and_save_PDF <-
  function(name_of_address_to_visit,
           name_of_where_to_save) {
    # Do the actual downloading of the PDF
    download.file(name_of_address_to_visit, name_of_where_to_save)
    # Helpful so that you know progress when running it on all the records
    print(paste("Done with", name_of_where_to_save, "at", Sys.time()))
    # Space out your requests so you don't overwhelm the website
    Sys.sleep(sample(15:30, 1))
  }
```

<!-- The next step is to remove the front matter from the PDFs.  -->

<!-- ```{r frontmatterexample, echo=TRUE, eval = FALSE} -->

<!-- get_text_from_PDFs <- -->
<!--   function(name_of_input_PDF_file, -->
<!--            name_of_output_csv_file) { -->
<!--     pdf_document <- pdf_text(name_of_input_PDF_file) -->
<!--     # Convert to tibble so that tidyverse can be used -->
<!--     pdf_document_tibble <- tibble(text = pdf_document) -->
<!--     rm(pdf_document) -->
<!--     # Each row is now a page of the PDF -->
<!--     # Adding a column of the row numbers allows you to keep track of the page numbers -->
<!--     pdf_document_tibble$pageNumbers <- 1:nrow(pdf_document_tibble) -->
<!--     # Separate each line (of each page) into own row -->
<!--     pdf_document_tibble <- -->
<!--       separate_rows(pdf_document_tibble, text, sep = "\\n") -->
<!--     # Identify page headers and footers and remove them -->
<!--     pdf_document_tibble <- pdf_document_tibble %>% -->
<!--       group_by(pageNumbers) %>% -->
<!--       mutate(lineNumber = 1:n()) %>% # This gives you a line numbering for each page -->
<!--       mutate(lastLine = n()) %>% # This tells you the number of the last line in each page -->
<!--       ungroup() -->
<!--     ## Identify front matter and remove it -->
<!--     pdf_document_tibble <- pdf_document_tibble %>% -->
<!--       mutate( -->
<!--         firstSpeakerRow = str_detect(text, "SPEAKER") -->
<!--       ) -->
<!--     pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == FALSE] <- NA -->
<!--     # Get the row and corresponding page and then filter to only pages from that page -->
<!--     row_of_first_SPEAKER <- -->
<!--       pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == TRUE] %>% which() %>% first() -->
<!--     first_page_of_interest_SPEAKER <- -->
<!--       pdf_document_tibble[row_of_first_SPEAKER, "pageNumbers"] %>% as.integer() -->
<!--     filter_from_here <- -->
<!--       case_when( -->
<!--         !is.na(first_page_of_interest_SPEAKER) ~ first_page_of_interest_SPEAKER -->
<!--       ) -->
<!--     pdf_document_tibble <- pdf_document_tibble %>% -->
<!--       filter(pageNumbers >= filter_from_here) %>% -->
<!--       select(-firstSpeakerRow) -->
<!--     # Save file -->
<!--     write_csv(pdf_document_tibble, name_of_output_csv_file) -->
<!--     # Helpful to know where you're up to -->
<!--     print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time())) -->
<!--   } -->

<!-- Then the rows need to be combined: -->
<!-- ```{r combinerows, echo=TRUE, eval = FALSE} -->
<!-- split_columns <- -->
<!--   function(name_of_input_csv_file, -->
<!--            name_of_output_csv_file) { -->
<!--     # Read in the csv, based on the filename list -->
<!--     csv_with_rows_to_combine <- -->
<!--       read_csv(name_of_input_csv_file, -->
<!--                trim_ws = FALSE, -->
<!--                col_types = cols()) -->
<!--     # Remove any extra whitespace i.e. two or more spaces and spaces at either end.  -->
<!--     # Yes, I know that I turned this off in the read_csv, but it's better to be  -->
<!--     #explicit because the whitespace is useful sometimes. -->
<!--     csv_with_rows_to_combine$text <- -->
<!--       str_squish(csv_with_rows_to_combine$text) -->
<!--     # Put everything onto one line, which allows us to rejoin words that have been  -->
<!--     #split across two lines e.g. Mon- ica -->
<!--     csv_with_rows_to_combine <- csv_with_rows_to_combine %>% -->
<!--       mutate(text = str_replace_all(text, "-$", "MONICA")) -->
<!--     full_days_hansard <- csv_with_rows_to_combine %>% -->
<!--       select(-pageNumbers) %>% -->
<!--       summarise(text = paste(text, collapse = " ")) %>% -->
<!--       mutate(text = str_replace_all(text, "MONICA ", "")) %>% -->
<!--       mutate(text = str_replace_all(text, "[:space:]-(?=[:alpha:])", " - ")) -->
<!--     rm(csv_with_rows_to_combine) -->
<!--     write_csv(full_days_hansard, name_of_output_csv_file) -->
<!--     print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time())) -->
<!--   } -->
<!-- ``` -->

<!-- Finally, we can fix the spelling: -->
<!-- ```{r fixspelling, echo=TRUE, eval = FALSE} -->
<!-- fix_spelling <- -->
<!--   function(name_of_input_csv_file, -->
<!--            name_of_output_csv_file) { -->
<!--     csv_to_clean <- -->
<!--       read_csv(name_of_input_csv_file, -->
<!--                trim_ws = FALSE, -->
<!--                col_types = cols()) -->
<!--     #Fix the spelling -->
<!--     csv_to_clean$text <- -->
<!--       stri_replace_all_regex( -->
<!--         csv_to_clean$text, -->
<!--         "\\b" %s+% fix_wrong_spellings$original %s+% "\\b", -->
<!--         fix_wrong_spellings$corrected, -->
<!--         vectorize_all = FALSE -->
<!--       ) -->
<!--     # Save file -->
<!--     write_csv(csv_to_clean, name_of_output_csv_file) -->
<!--     print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time())) -->
<!--   } -->
<!-- ``` -->

## Stopwords over time {#stopwordsgraph}
**[Insert the graph of stop words over time.]**

@@

@@

elections %>% 
  filter(election == 1) %>% 
  select(-election, -comment) %>% 
  kable("latex", booktabs = T, caption = "Elections") %>%
  kable_styling(font_size = 8)

@@

@@

@@

governments %>%
  rename(
    "Government" = "government",
    "Prime Minister" = "primeMinister",
    "Party" = "party",
    "Start" = "start",
    "End" = "end",
    "Died in Office" = "diedInOffice",
    "HoR" = "hor",
    "Senate" = "senate"
    ) %>% 
  kable(booktabs = T, caption = "Change in prime ministers") %>%
  kable_styling(font_size = 8) %>% 
  footnote(general = "This table contains summary information for each prime minister of Australia. HoR and Senate refer to the number of days that each chamber sat for while that person was prime minister.",
  footnote_as_chunk = T, 
    threeparttable = TRUE
           )

@@

@@

# Effect of number of topics on analysis model results {#resilientresults}

**[Add results for 60 and 100 topics.]**

>>>>

header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage[table]{xcolor}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{subfig}

@@

# elections <-
#   read_csv("../../../outputs/misc/misc_elections.csv", col_types = cols())

# governments <-
#   read_csv("../../../outputs/misc/pm_dates.csv", col_types = cols())

@@

The recent digitisation of the Canadian Hansard, @BeelenEtc2017, has allowed increased analysis of Canadian parliament text records. For instance, @RheaultCochran2018 examined ideology and party polarisation in Britain and Canada using word embeddings. A digitised version of the UK Hansard has been available for some time. For instance, @Duthie2016 examined which politicians made supportive or aggressive statements toward other politicians, and @PetersonSpirling2018 examined polarisation. One exciting aspect of research using the UK Hansard has been linking text records with other datasets. For instance, @SlapinKirklandLazzaroLeslie2018 linked votes and speeches to examine grandstanding within parties. Another exciting aspect is that as digitisation methods improve, increasingly older UK records can be analysed, for instance, @Dimitruk2018 considered the effect of estate bills on prorogations in seventeenth century England. In New Zealand, @Curran2018 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950.

@@

We use the official PDF release and the formatting of the Hansard records changes over time. We use scripts written in R [@R2018] to convert the PDFs into daily text records.[^scriptsfootnote] Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate, especially for older records. An example of the latter issue is that 'the' is often parsed as 'thc'. These errors are corrected when they can be identified.

[^scriptsfootnote]: The exact scripts that we use are available on request or via the GitHub repository for this paper. The scripts are primarily based on: the \texttt{PDFtools} R package of @Ooms2018pdftools; the \texttt{tidyverse} R package of @Wickham2017; the \texttt{tm} R package of @FeinererHornik2018; the \texttt{lubridate} R package of @GrolemundWickham2011; the \texttt{tidytext} R package of @SilgeRobinson2016; and the \texttt{stringi} R package of @Gagolewski2018. The functions of those packages are augmented by: the \texttt{furrr} R package of @VaughanDancho2018; and the \texttt{tictoc} R package of @Izrailev2014. The \texttt{hunspell} R package of @Ooms2017 is used to help find spelling issues; and the \texttt{quanteda} R package of @Benoit2018 is used to compound multiword expressions.

@@

@@

Define $\theta_{dp}$ to be the proportion of topic $p$ on day $d$. Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P = 80$ are equal to the estimated values of $\theta_d$ from the CTM. We assume that the majority of variation in topics is across sitting periods, $s$, where a sitting period is defined as any group of days that are less than one week apart. Using this definition, there are 822 sitting periods over the period 1901 to 2018 inclusive. Appendix \@ref(hansardsummarystatistics) contains more information about the sitting patterns over the course of the year, which have changed considerably since Federation.

@@

LDA output defines a topic as a distribution of probabilities over words. In Table \@ref(tab:topwords) we display the ten words with the highest association for each of the 80 topics, but the topics are defined by probability distributions over all words. LDA does not apply labels to each topic, or collection of words, instead this has to be done by inspection. The topics cover areas such as budgets, demography, transport and infrastructure, war and conflict, health, education, agriculture, and trade. Similar to when topic models are run using the parliamentary text records of other countries, there are also some topics that seem to be about procedural or day-to-day matters, such as Topics 7 or 9. As expected, some topics seem to somewhat overlap with their content: for instance, Topics 4, 26, 28, 30 and 66 all relate to war and conflict.

@@

top_words %>% 
  kable("latex", 
        booktabs = T, 
        longtable = TRUE, 
        caption = "The ten words most strongly associated with each topic"
        ) %>%
  kable_styling(font_size = 8, 
                latex_options = c("repeat_header")
                )
```

@@

```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with five topics highlighted", out.width = '100%'}
knitr::include_graphics("../../figures/topics_example.png", auto_pdf = FALSE)

@@

```{r threeexamples, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, for three periods", out.width = '100%'}
knitr::include_graphics("../../figures/topics_examples_three.png", auto_pdf = FALSE)
```

@@

```{r mugov, cache = TRUE, echo = FALSE, fig.cap = "Level effects for prime ministers by selected topics.", out.width = '100%'}
knitr::include_graphics("../../figures/mu_gov.pdf")
```

```{r muelection, cache = TRUE, echo = FALSE, fig.cap = "Level effects for election periods by selected topics", out.width = '100%'}
knitr::include_graphics("../../figures/mu_election.pdf")
```

<!-- In Appendix \@ref(resilientresults) we show that our main findings are resilient to both fewer - 60 - and more - 100 - topics. -->

@@

Of the 36 prime ministers over this period, we find that 20 of them are significantly different to the prime minister that preceded them. However, four of these results -- the significance of the Page premiership, the first Menzies premiership, the Chifley premiership and the Abbott premiership -- are likely due to the short length of either the prime minister or the predecessor and should be ignored, leaving only 16. The earliest of these are the first Fisher premiership, the Cook premiership and the third Fisher premiership, which were different to the second Deakin premiership, the second Fisher Premiership, and the Cook Premiership, respectively. To a certain extent this is likely due to changes due to World War I.

@@

By bringing a new dataset of what was said in the Australian Federal Parliament to bear for our analysis we are able to consider events over the full history of the Commonwealth of Australia. However even after cleaning the dataset remains imperfect and is more fit-for-purpose than of broad applicability. Future work could continue to improve the quality of this dataset. For instance, exploiting the available XML records to enhance the record parsed from the PDFs would enable the creation of a Hansard for research purposes that combined the best of both and was more useful for variety of research.

Using text as data allows us to conduct larger-scale analysis that would not be viable using less-automated approaches and so researchers may be able to identify associations and patterns that would otherwise have been overlooked. That said, the approach has well-known shortcomings and weaknesses, such as those documented by @GrimmerStewart2013.

Our paper should be considered a complement to more detailed analysis such as qualitative methods and case studies. An example of one of the more glaring issues when using topic models is the need to interpret the topics. This can be difficult, especially when the number of topics is large, but in a dataset of the size that we have, a large number of topics is needed. Also, although topic modelling is an unsupervised machine learning technique, the inputs require fine-tuning. Most obviously the number of topics needs to be specified, but there are also more nuanced aspects to be aware of. For instance, selecting stop words for removal and which words to merge because of common co-location has an impact on the topics. Even after doing this there tend to be topics that are not overly meaningful, especially on their own. One way to get around using topic models is to use a supervised learning approach, such as that used by @AshMorelliOsnabru2018 in the context of New Zealand Hansard. Another is to use the words more directly, for instance word2vec and other approaches. As computational power become cheaper and more appropriate analytical methods, such as @Taddy2015 as applied in @GentzkowShapiroTaddy2018 in the context of examining congressional speech records from 1873 to 2016 to find that partisanship has risen in the past few decades, are developed this becomes a more feasible options and future research could explore that direction.

@@

Watching Australian politicians at work can sometimes be a little disheartening. It can be hard to believe that not only are those in charge shouting insults that would not be tolerated in a schoolyard, but that the electorate voted to put them there. Nonetheless, our work suggests that important topics are discussed in parliament. It is easy to look back and think that we live in uniquely tumultuous times, but our analysis suggests events have always driven debate and that periods of stability may be the exception. However, we do find that since the 1990s the effect of prime ministers and elections on the topics discussed in the Australian parliament does seem more pronounced than it used to be.

@@

The distribution of sitting days over the course of the year changes over time (Figure \@ref(fig:allsittingdaysplotted)).

```{r allsittingdaysplotted, echo=FALSE, fig.cap="All sitting days", out.width = '100%'}
knitr::include_graphics("../../figures/sitting_dates_all.pdf")
```

It was initially more piecemeal. This can be seen by comparing the pattern of sitting days in the years to 1920 (Figure \@ref(fig:dayssattonineteentwenty)) with those in the 19 years from, and including, 2000 (Figure \@ref(fig:dayssatfromtwothousand)).

@@

## Stopwords over time {#stopwordsgraph}

Figure \@ref(fig:stopwordsproportion) shows the proportion of five common words -- 'and', 'be', 'of', 'the', 'to' -- compared with the total number of words over time.

```{r stopwordsproportion, echo=FALSE, fig.cap="Proportion that some common words comprise of all words, over time", out.width = '100%'}
knitr::include_graphics("../../figures/stop_words.pdf")
```

@@

The first of the two types of events that we consider in this paper is an election (Table \@ref(tab:elections)).

@@

read_csv("../../../outputs/misc/misc_elections.csv", col_types = cols())  %>% 
  filter(election == 1) %>% 
  select(-election, -comment) %>%
  select(election_count, everything()) %>% 
  rename(
    "Number" = "election_count",
    "Year" = "year", 
    "Date" = "electionDate", 
    "Total seats" = "seatsTotalNumber", 
    "Winner" = "electionWinner"
    ) %>%  
  kable("latex", 
        booktabs = T, 
        longtable = TRUE, 
        caption = "List of Australian elections"
        ) %>%
  kable_styling(font_size = 8) %>% 
  footnote(
    general = "This table contains summary information for each prime minister of Australia. HoR and Senate refer to the number of days that each chamber sat for between elections.",
    footnote_as_chunk = T, 
    threeparttable = TRUE
    )

@@

Between 1901 and 2018 there are 45 elections, roughly one every two to three years. All of the election periods have a reasonable number of sitting days within them. The fewest was the election on 17 November 1928, with only 40 sitting days in the House of Representatives and 29 in the Senate, as there was another election almost a year later on 12 October 1929.

The number of seats increases from 74 to 121 at the 10 December 1949 election, having been reasonably consistent to that point. Another large increase in the number of seats, this time from 125 to 148, happens at the 1 December 1984 election.

In the first half of our sample especially, the name of the major opposition party changes. For this reason we distinguish between the Labor Party, and the non-Labor Party in terms of who won the election, that is which party was able to form government.

@@

The second of the two types of events that we consider in this paper is a change in prime minister (Table \@ref(tab:governments)).

@@

read_csv("../../../outputs/misc/pm_dates.csv", col_types = cols()) %>%
  rename(
    "Government" = "government",
    "Prime Minister" = "primeMinister",
    "Party" = "party",
    "Start" = "start",
    "End" = "end",
    "Died in Office" = "diedInOffice",
    "HoR" = "hor",
    "Senate" = "senate"
    ) %>% 
  kable(booktabs = T, 
        longtable = TRUE, 
        caption = "List of Australian prime ministers"
        ) %>%
  kable_styling(font_size = 8
                ) %>% 
  footnote(general = "This table contains summary information for each prime minister of Australia. HoR and Senate refer to the number of days that each chamber sat for while that person was prime minister.",
  footnote_as_chunk = T, 
    threeparttable = TRUE
           )

@@

Between 1901 and 2018 30 different people have been prime minister. Four of those---Deakin, Fisher, Menzies and Rudd---returned to the primiership at least once after being replaced, meaning Scott Morrison defines the 36th prime ministerial period.

Three people have died while prime minister: Lyons in 1939, Curtin in 1945, and Holt in 1967. Their respective immediate successors were only prime minister for a short period. As such, we do not consider them when determining the neighbouring prime minister. Specifically, we compare: the first Menzies premiership with Lyons instead of Page; Chifley with Curtin instead of with Forde; and Gorton with Holt instead of with McEwan.

The other prime ministerial period that we do not consider in this paper is the second Rudd premiership This is because it only contained a few sitting days. That is, we compare Tony Abbot with Julia Gillard.

@@

<!-- # Effect of number of topics on analysis model results {#resilientresults} -->

<!-- **[Add results for 60 and 100 topics.]** -->
